---
title: "Progress Memo 2"
subtitle: |
  | Final Project 
  | Data Science 1 with R (STAT 301-1)
author: "Nikole Montero Cervantes"
date: today

format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: false
  warning: false

from: markdown+emoji 
---

::: {.callout-tip icon=false}

## Github Repo Link

[https://github.com/stat301-1-2023-fall/final-project-1-Nikole26.git](https://github.com/stat301-1-2023-fall/final-project-1-Nikole26.git)

:::

```{r}
#| label: Loading packages
library(tidyverse)
library(skimr)
library(stringr)
library(ggplot2)
library(plotly)
library(tidyr)
library(knitr)
library(ggrepel)
library(kableExtra)
```

```{r}
#| label: Load packages
data <- read_csv("data/tripadvisor_european_restaurants.csv")
```

# Introduction



# Overview of te data

This dataset was acquired through scraping TripAdvisor (TA), a well-known travel website, for its restaurant information. The dataset contains a pool of 1,083,397 restaurants across European countries. There are 42 variables, among these variables, 25 are categorical and 17 are numericals. The raw datasets for Europe's largest cities were then carefully selected and combined for further examination.

It is important to note that this dataset comprises only those restaurants registered in the TripAdvisor database. Thus, it might not encompass all the restaurants within a city because the dataset relies solely on the TripAdvisor database.

# Cleaning the data

```{r}
data_tidy_1 <- data %>%
  rename(
    vegetarian = vegetarian_friendly,
    vegan = vegan_options,
    gluten_free = gluten_free
  ) %>%
  mutate(
    awards = ifelse(is.na(awards), "none", awards),
    special_diets = case_when(
      vegetarian == "Y" ~ "vegetarian",
      vegan == "Y" ~ "vegan",
      gluten_free == "Y" ~ "gluten_free",
      TRUE ~ "None"
    )) %>%
  select(-vegetarian, -vegan, -gluten_free) 

data_tidy_1 <- data_tidy_1 |>
  mutate(price_level = case_when(
    price_level == "€€€€" ~ "expensive",
    price_level == "€€-€€€" ~ "mid-range",
    price_level == "€" ~ "cheap",
    TRUE ~ price_level  # Keep other values unchanged
  ))

data_tidy_1$top_tags <- str_split(data_tidy_1$top_tags, ", ", simplify = FALSE)

data_tidy_1$top_tags <- lapply(data_tidy_1$top_tags, function(tags) {
  tags <- tags[!(tags %in% c("Vegetarian Friendly", "Vegan Options", "Gluten Free Options",
                             "Cheap Eats", "Mid-range", "Fine Dining"))]
  if (length(tags) == 0) {
    tags <- NA
  }
  tags
})

data_tidy_2 <-  data_tidy_1 |>
  mutate(
    minimum_range = as.numeric(str_extract(price_range, "\\d+(\\.\\d+)?")),
    maximum_range = as.numeric(str_extract_all(price_range, "\\d+(\\.\\d+)?") %>% sapply(function(x) x[2])),
    avg_price = (minimum_range + maximum_range) / 2
  ) |>
  select(-c(minimum_range, maximum_range))

data_tidy_2$top_tags <- lapply(data_tidy_2$top_tags, function(tags) {
  tags[tags %in% c("Brew Pub", "Wine Bar", "Pub")] <- "Bar"
  
  tags[tags %in% c("Pizza", "Northern Italy", "Southern Italy",
                   "Nepalese", "Vietnamese", "Hong Kong", "Thai", "Bangladeshi",
                   "Cantonese", "Zhejiang", "Japanese", "Sushi", "Asian",
                   "Mongolian", "Egypt", "Egyptian", "Balti", "Philippine",
                   "Tuscan", "Indian", "Tibetan", "Fujian", "Indonesian",
                   "Korean", "Hubei", "Turkish", "Russian", "Taiwanese", 
                   "Persian", "Middle Eastern", "Lebanese", "Cambodian",
                   "Japenese", "Pakistani", "Szechuan", "Chinese")] <- "Asia"
  
  tags[tags %in% c("Welsh", "Scottish", "Irish", "European", "French",
                   "Italian", "Mediterranean", "British", "Central-Italian",
                   "Dutch", "Greek", "Portuguese", "Czech", "Scandinavian", 
                   "Central European", "Danish", "Romanian", "Lombard",
                   "Ligurian", "Sicilian", "Polish", "Sardinian", "Campania",
                   "Neapolitan", "Austrian", "German", "Belgian", "Southern-Italian",
                   "Basque", "Turkish", "Apulian", "Russian", "Romana",
                   "Northern-Italian", "Southwestern", "Norwegian", "Scandinavian",
                   "Eastern European", "Moroccan", "Armenian", "Swiss", "Spanish",
                   "Catalan")] <- "Europe"
  
  tags[tags %in% c("Egyptian", "Egypt", "African", "Algerian", "Contemporary",
                   "Arabic", "Tunisian")] <- "Africa"
  
  tags[tags %in% c("Chilean", "Venezuelan", "Peruvian", "South American",
                   "Argentinian", "Latin", "Brazilian")] <- "South America"
  
  tags[tags %in% c("Mexican", "Central American", "Native American", "Cuban", "Latin",
                   "Caribbean", "Canadian", "American")] <- "North America"
  
  tags[tags %in% c("New Zealand", "Polynesian", "Australian")] <- "Oceania"
  
  tags <- tags[!(tags %in% c("Delivery Only", "Dinner", "Diner", "Healthy", "Barbecue", "Caucasian",
                             "Quick Bites", "Cajun & Creole", "International", "Deli", "Dessert",
                             "Bakeries", "Fast food", "Cafe", "Street Food", "Seafood", "Gastropub", 
                             "Dining bars", "Grill", "Steakhouse", "Beer restaurants",
                             "Halal", "Soups", "Speciality Food Market"))]
  
  if (length(tags) == 0) {
    tags <- NA
  } else {
    tags <- paste0(unique(tags), collapse = ", ")
  }
  
  tags
})

rows_NA <- data_tidy_2 |>
  summarise(across(everything(), ~sum(is.na(.))))

data_tidy_3 <- select(data_tidy_2, -address, -original_location, 
                      -keywords, -features, -cuisines, -popularity_detailed, 
                      -popularity_generic, -price_range, -original_open_hours)

data_final <- data_tidy_3[rowSums(!is.na(data_tidy_3)) > 24, ]

data_final <- na.omit(data_final, cols = "average_price")

data_final <- data_final |>
  rename(cuisines = top_tags,
         food_rating = food,
         value_rating = value,
         service_rating = service)
```

In the process of cleaning the data, various essential string manipulation, functions and transformation techniques were employed using the dplyr and stringr packages in R. The dataset underwent a series of refinements to enhance its tidiness and facilitate downstream analyses. Key steps in the cleaning process include:

• Variable Renaming

• Creating and Modifying Variables

• Handling Categorical Data

• Text Processing

• List Manipulation

• Numeric Extraction

• Data Filtering and Handling Missing Values


