---
title: "Progress Memo 1"
subtitle: |
  | Final Project 
  | Data Science 1 with R (STAT 301-1)
author: "Nikole Montero Cervantes"

format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: false
  warning: false

from: markdown+emoji 
---
  
::: {.callout-tip icon=false}

## Github Repo Link

[https://github.com/stat301-1-2023-fall/final-project-1-Nikole26.git](https://github.com/stat301-1-2023-fall/final-project-1-Nikole26.git)

:::

::: {.callout-warning}
GitHub (free account) cannot store large files. If you try to commit and push a large dataset you will have an ERROR! Any file over 100 MB (100,000 KB) needs to be added to the `.gitignore` file BEFORE committing.

**We may need to do that for files in your final project!**
:::

## Loading data
```{r}
library(skimr)
```


```{r}
library(tidyverse)

tripadvisor_european_restaurants <- read_csv("data/tripadvisor_european_restaurants.csv")
```


## Data source

This dataset was acquired through scraping TripAdvisor (TA), a well-known travel website, for its restaurant information. Raw data was collected utilizing a Python script that collected information from TripAdvisor restaurant listing pages through the pandas and BeautifulSoup libraries. The raw datasets for Europe's largest cities were then carefully selected and combined for further examination.

It is important to note that this dataset comprises only those restaurants registered in the TripAdvisor database. Thus, it might not encompass all the restaurants within a city because the dataset relies solely on the TripAdvisor database.

This dataset was sourced from Damien Beneschi on Kaggle, a platform dedicated to data science.

## Why this data

Having travelled to Eroupe before, I have been fascinated for its culture, but mainly their cuisine. I have tried many resutarintst in Europe usually following the recommendations and reviews from TripAdvisor. Thus, I wanted to do some deeper research on that how those all different variables come to play and which are the best resutauratn or the most affordible one for people that loves backapacking, but still get a quality dish. 

## Data quality & complexity check

data quality observations:
- rename the price range is important to make it more understandble
- organizing the cuisine style coulumn is important since there are too many valuesper restaurant. Skimming throguh the data it seems neccesary creating maybe a nyew varibale concerning dietary restrictions. And limitating to cusine style to three options regarding the nationaloty of food they provide to make it more readable and easy to anaylise. 
- Another complet


## Potential data issues

The main potential issue 
- There is some missing values for some restauratns. 
- Some rows have empty valus, such as NA is not recognized but either it is just left in blank, so it's important to clean the data. 



## Misc

Mention in the memo that if the dataset is too large and difficult to work with, you will randomly select a smaller subset. **Verify with professor if this is ok**
^ called Downsampling
