---
title: "Progress Memo 1"
subtitle: |
  | Final Project 
  | Data Science 1 with R (STAT 301-1)
author: "Nikole Montero Cervantes"

format:
  html:
    toc: true
    embed-resources: true
    
execute:
  echo: false
  warning: false

from: markdown+emoji 
---
  
::: {.callout-tip icon=false}

## Github Repo Link

[https://github.com/stat301-1-2023-fall/final-project-1-Nikole26.git](https://github.com/stat301-1-2023-fall/final-project-1-Nikole26.git)

:::


## Loading libraries and data

```{r}
#| echo: true
# Loading libraries 
library(tidyverse)
library(skimr)

# Loading data 
tripadvisor_european_restaurants <- read_csv("data/tripadvisor_european_restaurants.csv")
```


## Data source

This dataset was acquired through scraping TripAdvisor (TA), a well-known travel website, for its restaurant information. The dataset contains a pool of 1,083,397 restaurants across European countries. The raw datasets for Europe's largest cities were then carefully selected and combined for further examination.

It is important to note that this dataset comprises only those restaurants registered in the TripAdvisor database. Thus, it might not encompass all the restaurants within a city because the dataset relies solely on the TripAdvisor database.

This dataset is credited to Stefano Leone on Kaggle, a platform dedicated to data science.

## Why this data?

Having travelled to Europe before, I have been fascinated for its culture, but mainly their cuisine. Throughout my journeys, I've explored numerous European restaurants, often relying on recommendations and reviews from platforms like TripAdvisor. Thus, I'm curious about the complex interactions between many elements that go into creating a truly exceptional dining experience. The problem of locating the best eateries that satisfy budget-conscious travelers without sacrificing excellent food quality really piqued my interest. I want to dive into the affordable restaurants with great food, making travel experiences better for people like me who love exploring food while traveling.

## Skim and glimpse at the data

```{r}
#| echo: false
skim_without_charts(tripadvisor_european_restaurants)
glimpse(tripadvisor_european_restaurants)
```


## Data quality & complexity check

This dataset contains 1,083,397 observations and 42 variables. Among these variables, 25 are categorical and 17 are numericals. 

It is important to organize the price range and price level category by potentially mutating the values to enhance its clarity and user-friendliness. Simultaneously, organizing the cuisine style column is vital due to the excessive number of values associated with each restaurant. Reviewing the data, it becomes evident that creating a new variable related to dietary restrictions is necessary. This approach not only ensures a more organized dataset but also prevents the unnecessary proliferation of additional columns, streamlining the information and enhancing its overall efficiency.

## Potential data issues

The presence of missing values in various variables is the main potential issues for this data analysis. This issue can undermine the reliability of the results, leading to unaccurate interpretations. To address this problem, a systematic approach needs to be implemented. Firstly, identifying the variables with missing values and understanding the patterns behind these gaps is essential. Once the patterns are discerned, I will clean the data by getting rid of the rows with most of NA values. So, the missing data issue can be mitigated, ensuring a more comprehensive and reliable dataset for analysis and interpretation.


## Misc

Considering that this is a large data, if the dataset proves to be excessively large and challenging to work with, a viable solution is to randomly select a smaller subset, called downsampling. Downsampling involves randomly selecting a smaller subset from the extensive dataset, making it more manageable for analysis purposes. This strategic approach ensures that the analysis remains feasible and efficient, even when dealing with vast datasets. 